Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-03-11 hotstorage13/eval.tex
fix typos

Table~\ref{tab:overall} shows performance change when memory limit $M$=35MB is imposed and
the number of parititons per machine ($q$) varies from 50 to 1500.
Row 2 is the memory space required to load a partition of global index and detection requests.
When $q=50$, the required memory is 156MB, which  is  not  a viable choice  under  constraint $M=$35MB.  
Row 3 is the parallel time and Row 4 is  the aggregated throughput of  100 nodes.
%The result shows the backup with multi-phase deduplication  for all VM images can be completed in about 3.09 hours
%with the very small resource usage.
Row 5 is  the parallel time if  we use Option 1 with $p\times q$ send buffers 
described in Section~\ref{sect:arch}. 
With the large number of buffers, the available space per buffer reduces significantly as $q$ increases, which leads to
a big increase of IO requests and seek cost.

>>>>

Table~\ref{tab:overall} shows performance change when memory limit $M$=35MB is imposed and
the number of partitions per machine ($q$) varies from 50 to 1500.
Row 2 is the memory space required to load a partition of global index and detection requests.
When $q=50$, the required memory is 156MB, which  is  not  a viable choice  under  constraint $M=$35MB.  
Row 3 is the parallel time and Row 4 is  the aggregated throughput of  100 nodes.
%The result shows the backup with multi-phase deduplication  for all VM images can be completed in about 3.09 hours
%with the very small resource usage.
Row 5 is  the parallel time if  we use Option 1 with $p\times q$ send buffers 
described in Section~\ref{sect:arch}. 
With the large number of buffers, the available space per buffer reduces significantly as $q$ increases, which leads to
a big increase of IO requests and seek cost.
